Tracing the Hercules stream around the Galaxy

### 2010-05-20 tex/hercules.tex
groups-simulations: rearrange the reference

The astrometric \Gaia\ mission will measure the parallaxes and proper
motions of up to one billion stars, most of which will be disk
stars. With parallax and proper motion accuracies down to 10
microarcseconds, \Gaia\ will be able to probe the kinematics of the
disk out to several kpc in all directions
\citep{bailerjones08a}. Crucially, it will provide large samples of
stars in many of the promising regions in
\figurename~\ref{fig:rphi2d}, which will be able to verify the
predictions laid out in this paper and will allow the dynamical
properties of the bar to be tightly constrained, something that will
be hard for \Gaia\ to do using direct observations of the bulge due to
the large extinction toward the Galactic center.

@@

>>>>

The astrometric \Gaia\ mission will measure the parallaxes and proper
motions of up to one billion stars, most of which will be disk
stars. With parallax and proper motion accuracies down to 10
microarcseconds, \Gaia\ will be able to probe the kinematics of the
disk out to several kpc in all directions
\citep{bailerjones08a}. Crucially, it will provide large samples of
stars in many of the promising regions in
\figurename~\ref{fig:rphi2d}, which will be able to verify the
predictions laid out in this paper and will allow the dynamical
properties of the bar to be tightly constrained, something that will
be hard for \Gaia\ to do using direct observations of the bulge due to
the large extinction toward the Galactic center \citep{robin05a}.

@@

\bibitem[Robin \etal(2005)]{robin05a}
  Robin,~A.~C., \etal, 2005,
  \aap, 430, 129
